This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-02 article.tex
Added to the title
More text about DEFLATE

\title{This PDF is a Git Repository\\Containing its Own \LaTeX\ Source}
\author{Evan Sultanik}
\date{April 11, 2017}

@@

\section{The Git Bundle File Format}

@@

I hope you like Soviet holes, dear neighbor, because chasing this
rabbit might remind you of \includegraphics{kolskaya}. I think it is
useful to describe the git packfile format here, since it is not well
documented elsewhere. If that doesn't interest you, it's safe to skip
to the next section.

\begin{center}
\includegraphics[width=0.5\hsize]{RazvodityeKrolikov_small}
\end{center}

@@

\item Adobe, being Adobe, will refuse to open the polyglot unless the PDF is version 1.4 or earlier.  I guess it doesn't like some element of the git bundle signature or digest if it's PDF~1.5? Why? Because Adobe, that's why.

@@

>>>>

\title{This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself}
\author{Evan Sultanik}
\date{April 11, 2017}

@@

\section{The Git Bundle File Format}
\label{sec:GitBundleFormat}

@@

Although not entirely required to understand the polyglot, I think it
is useful to describe the git packfile format here, since it is not
well documented elsewhere. If that doesn't interest you, it's safe to
skip to the next section.  But if you do proceed, I hope you like
Soviet holes, dear neighbor, because chasing this rabbit might remind
you of \includegraphics{kolskaya}.

\begin{center}
\includegraphics[width=0.33\hsize]{RazvodityeKrolikov_small}
\end{center}

@@

\item Adobe, being Adobe, will refuse to open the polyglot unless the PDF is version 1.4 or earlier.  I guess it doesn't like some element of the git bundle signature or digest if it's PDF~1.5. Why? Because Adobe, that's why.

@@

So, where can we put a 5-byte DEFLATE header such that it won't
corrupt the PDF? We could use our standard trick of putting it in a
PDF object stream that we've exploited countless times before to
enable PoC$\|$GTFO polyglots. The trouble with that is that object
streams are fixed-length, so once the PDF is decompressed
(\textit{i.e.},~when a repo is cloned from the git bundle), then all
of the 5-byte DEFLATE headers will disappear and the object stream
lengths would all be incorrect. Instead, I chose to use PDF comments,
which start at any occurrence of the percent sign character~(\%)
outside a string or stream and continue until the first occurrence of
a newline.  All of the PDF viewers I tested don't seem to care if
comments include non-ASCII characters; they seem to simply scan for a
newline. Therefore, we can inject ``\texttt{\%\textbackslash n}''
between PDF objects and move the DEFLATE headers there. The only
caveat is that the DEFLATE header itself can't contain a newline
byte~(\texttt{0x0A}), otherwise the comment would be ended
prematurely.  We can resolve that by adding extra spaces to the end of
the comment, increasing the length of the following DEFLATE block and
thus increasing the length bytes in the DEFLATE header and avoiding
the \texttt{0x0A}. The only concession made with this approach is that
PDF Xref offsets in the deflated version of the PDF will be off by a
multiple of 5, due to the removed DEFLATE headers. Fortunately, most
PDF readers can gracefully handle incorrect Xref offsets (at the
expense of a slower loading time), and this will only affect the PDF
contained in the repository, \emph{not} the PDF polyglot.
